\cvsection{Work Experience}
        \cvexperience{Software Engineer}{Moon}{Sept 2021 – Aug 2022}{Hooli}{\footnotesize\faCode \hspace{1pt}      \cvtag{\textbf{C}}\cvtag{C++}\cvtag{C\#}\cvtag{R}\cvtag{F}\cvtag{T}}
	\begin{itemize}
            \item Engineered modern applications with Java, JavaScript, SQL Server, and No SQL.
            \item Led a team of 5 junior software engineers undertaking the software development life cycle for 9 bespoke client projects.
            \item Built innovative user account control (UAC) features into new products to exceed industry standards and achieve 100\% compliance with best practices.
	\end{itemize}
        Slashed security breaches by an average of \textbf{81\%} for all clients.
	
	\medskip

         \cvexperience{Senior Web Developer / Systems Architect}{Saturn \href{https://solarsystem.nasa.gov/planets/saturn/overview/}{\faExternalLink*}}{Jan 2015 – Aug 2021}{New Enterprise}{\footnotesize\faCode \hspace{1pt}      \cvtag{\textbf{Node.js}}\cvtag{\textbf{PHP}}\cvtag{\textbf{Python}}\cvtag{Laravel}}
        Produced a device to \textbf{avoid the improper occupation of parking spaces} reserved for \textbf{people with disabilities}.
	\begin{itemize}
		\item Structure several internal systems comprising order entry/management tools, conversion/revenue reporting, and production workflow tracking, as well as designed custom REST APIs built in Python, Laravel PHP, and NodeJS.
            \item Successfully installed Linux servers and virtualized environments using Docker, Hyper-V, and Amazon Web Services.
            \item Designed and implemented PHP web application, streamlining high-server traffic resource configuration and allocation.
	\end{itemize}
        	
	\medskip
	
	\cvexperience{Senior Programmer}{Venus}{ Jun 2013 – Dec 2014}{Ecommerce Agency}{\footnotesize\faCode\hspace{1pt} \cvtag{\textbf{Unix}}\cvtag{PHP 5}\cvtag{MySQL}\cvtag{CSS}}
	\begin{itemize}
		\item Successfully generated back-end programming utilizing LAMP stack; Linux (CentOS 5/Redhat), Apache with Kohana 2, PHP 5, CSS, JavaScript/jQuery, and MySQL frameworks.
            \item Created e-commerce sites integrated with PayPal, Authorize.net, and other payment gateway APIs.
		\item Provided leadership as a subject matter expert (SME) on hosting issues, client and staff logins, and general upgrades/maintenance of servers.
	\end{itemize}